Improved association in a classical density functional theory for water

### 2014-01-17 papers/water-saft/paper.tex
more (final?) changes to water paper Tested on knightley. Took 1:00.12.

Finally, in order to compare with experimental results, we examined
the hydration of Krypton.  We use a Lennard-Jones potential with
values $\epsilon = .9518$\fixme{units} and $\sigma = 3.42 \AA$ with mixing rules
and values from\cite{paschek2004temperature} where the water
parameters are based on SPC calculations. Figure~\ref{fig:g-Kr} shows a
comparison of the krypton-oxygen partial radial
distribution($g_{Kr-O}$) from the functional in this work and on
created from the functional of \hughesetal\ with experiment
\cite{bowron1998hydrophobic}.  The new functional shows an improvement
in the height of the first peak, and the general shape of $g_{O-Kr}$
compare to that of \hughesetal \

>>>>

Finally, in order to compare with experimental results, we examined
the hydration of Krypton.  To describe the interaction of water with
krypton, we use a Lennard-Jones potential with values $\epsilon =
.9518$~kJ/mol and $\sigma = 3.42$~\AA\ calculated using the
Lorentz-Berthelot mixing rules and the Lennard-Jones parameters for
water from SPC/E
calculations~\cite{paschek2004temperature}. Figure~\ref{fig:g-Kr}
shows the krypton-oxygen partial radial distribution function
$g_{Kr-O}(r)$, which gives the relative probability density that an
oxygen atom resides at a distance $r$ from a krypton atom centered at
the origin.  We present theoretical curves computed using both this
work and the functional of \hughesetal, which we compare with
experimental data from extended x-ray absorption fine structure
spectroscopy~(EXAFS)~\cite{bowron1998hydrophobic}.  The new functional
shows improved agreement with experiment in the height and position
of the first maximum as well as the hight and position of the first
minimum in $g_{Kr-O}(r)$ when compared with that of \hughesetal \
